Fit by design: Developing seed–substrate combinations to adapt dike grasslands to microclimatic variation

### 2023-08-03 manuscript.Rmd
Reduce dpi of figure 2

```{r fig.id = "nmds", fig.asp = 0.9696, fig.width = 6.49, fig.cap = ""}
knitr::include_graphics(
  here::here("outputs", "figures", "figure_2_nmds_500dpi_16.5x16cm.tiff")
  )
```

@@

```{r fig.id = "interactions", fig.asp = 1.2121, fig.width = 6.49, fig.cap = ""}
knitr::include_graphics(
  here::here("outputs", "figures", "figure_4_500dpi_16.5x20cm.tiff")
  )
```

>>>>

```{r fig.id = "nmds", fig.asp = 0.9696, fig.width = 6.49, fig.cap = ""}
knitr::include_graphics(
  here::here("outputs", "figures", "figure_2_nmds_300dpi_16.5x16cm.tiff")
  )
```

@@

```{r fig.id = "interactions", fig.asp = 1.2121, fig.width = 6.49, fig.cap = ""}
knitr::include_graphics(
  here::here("outputs", "figures", "figure_4_300dpi_16.5x20cm.tiff")
  )
```
